### 2021-07-21 src/paper/data/synthetic_population.tex
Version 5: Final long version  (#4)

% school
Every child that goes to school is part of three different classes that meet every day on
weekdays when there are no vacations and no school policies are in place.\footnote{We
implement vacations on the federal state level.} Each class consists of approximately 23
students \citep{OECD2013} and two teachers. All students in a class are of the same age
and live in the same state and mostly also in the same county. In addition, each
child gets assigned a value that captures his or her need to attend nursery, preschool or
school. This allows us to capture various degrees of emergency care that can be granted
while educational facilities are closed or are on some kind of rotating schedule.

>>>>

% school
Every child that goes to school is part of a school class. Each school class meets
three times per weekday, each time with a different set of two teachers, unless
there are vacations or policies that suspend schools.\footnote{We
implement vacations on the federal state level.} Each class consists of approximately 23
students \citep{OECD2013}. All students in a class are of the same age
and live in the same state and mostly also in the same county. In addition, each
child gets assigned a value that captures his or her need to attend nursery, preschool or
school. This allows us to capture various degrees of emergency care that can be granted
while educational facilities are closed or are on some kind of rotating schedule.

### 2021-07-21 src/paper/model/number_of_contacts.tex
Version 5: Final long version  (#4)

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only those 50
people had contact with an infectious person and the disease has an infection probability
of one or whether everyone met one infectious person but the disease has an infection
probability of only 5 percent per contact. SEIR models do not distinguish between the
number of contacts and the infectiousness of each contact. Instead, they combine the two
into one parameter that is not invariant to social distancing policies.

To model social distancing policies, we need to disentangle the effects of the number of
contacts of each individual and the effect of mostly policy-invariant infection
probabilities specific to each contact type. Since not all contacts are equally
infectious, we distinguish different contact types.

@@

In our empirical application we distinguish the following  contact types that
are depicted in Figure~\ref{fig:model_contacts_infections} and can be further grouped
in the categories household, work, education and others.

types of contacts:

@@

    \item Recurrent work contacts, capturing contacts with coworkers, repeating
          clients and superiors. Some of these recurrent contacts take place on
          every workday, others just once per week.

    \item Random work contacts: Working adults have contacts with randomly drawn other
          people, which are assortative in geographical location and age.

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet six teachers everyday and some of the teachers meet each other.

    \item Preschools: Children who are at least three years old and younger than six may
    attend preschool. Each group of nine children interacts with the same two adults
    every day. The children in each group are of the same age. The remaining mechanics
    are similar to schools.

    \item Nurseries: Children younger than three years may attend a nursery and interact
    with one adult. The age of the children varies within groups. The remaining
    mechanics are similar to schools.

    \item Random other contacts: Contacts with randomly drawn other
    people, which are assortative with respect to geographic location and and age group.
    This contact type reflects contacts during leisure activities, grocery shopping,
    medical appointments, etc..

    \item Recurrent other contacts representing contacts with friends neighbors or
        family members who do not live in the same household. Some of these contacts
        happen daily, others only once per week.

@@

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{subsec:data_number_of_contacts}. In particular, we sample the number of
contacts or group sizes from empirical distributions that sometimes depend on age. It
would also be possible to use economic or other behavioral models to predict the number
of contacts.

>>>>

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only those 50
people had contact with an infectious person and the disease has an infection probability
per contact ($\beta$) of one or whether everyone met one infectious person but the
disease has an infection probability of only 5 percent per contact. SEIR models do not
distinguish between the number of contacts ($\eta$) and the infectiousness of each
contact ($\beta$). Instead, they combine the two into one parameter that is not invariant
to social distancing policies.

To model social distancing policies, we need to disentangle the effects of the number of
contacts of each individual and the effect of mostly policy-invariant infection
probabilities specific to each contact type.

@@

In our empirical application we distinguish the following  contact types that
are depicted in Figure~\ref{fig:model_contacts_infections} and can be further grouped
in the categories household, work, education and others:

@@

    \item Recurrent work contacts: These capture contacts with coworkers, repeating
          clients and superiors. Some of these recurrent contacts take place on every
          workday, others just once per week. The contacts are assortative in
          geographical location and age.

    \item Non recurrent work contacts: Working adults have contacts with randomly drawn
          other people, which are assortative in geographical location and age.

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age and mostly
    live in the same county. Schools are closed on weekends and during vacations, which
    vary by states. School classes also meet six teachers every day and some of the
    teachers meet each other.

    \item Preschools: Children who are between three and six years old attend preschool.
    Each group consists of nine children of mixed ages and two adults who live mostly in
    the same county. They all meet each other every work day when there are no vacations.

    \item Nurseries: Children younger than three years may attend a nursery and interact
    with one adult. The age of the children varies within groups but all live in the same
    county. They all meet each other every work day when there are no vacations.

    \item Non recurrent other contacts: Contacts with randomly drawn other
    people, which are assortative with respect to geographic location and and age group.
    This contact type reflects contacts during leisure activities, grocery shopping,
    medical appointments, etc..

    \item Recurrent other contacts representing contacts with friends neighbours or
    family members who do not live in the same household. Some of these contacts happen
    daily, others only once per week. They are assortative in geographic location and
    age.

@@

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{subsec:data_number_of_contacts}. In particular, we sample the number of
contacts or group sizes from empirical distributions. It would also be possible to use
economic or other behavioral models to predict the number of contacts.

### 2021-07-21 src/paper/results/rapid_tests_statistics.tex
Version 5: Final long version  (#4)

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case,\comment[id=HM]{I do not
understand. 80 fals neg for 200 true pos does not seem too reliable? I guess the
important bit is the reference cat. -- catching 200 pos vs. nothing} which can be seen
from the number of false negative tests. At its peak at the beginning of May, there are
more than 80 false negative rapid tests per million inhabitants per day. While this
number might sound low in isolation, it becomes quite large when set in context: We
estimate that at at the the same time only 200 cases per million are detected by rapid
tests. This means that even at the time where discovery of cases via rapid tests is at
its peak, almost 30\% of people who are infected and make a test are not discovered by
the test.

This shows clearly that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are infected. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.

>>>>

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, one has to differentiate between the reliability of
one test in isolation and the effect imperfect tests can have when employed at a large
scale. On average our tests have a sensitivity of slightly more than 70\%. This means
they miss almost 30\% of infections among the tested. Of course perfect tests would have
an even larger effect but the relevant number to compare is that up to 200 cases per
million are detected by rapid tests every day which would have otherwise gone undetected.

This clearly shows that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are infected. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.
